### 2020-03-26 Strings2020/strings2/strings2.tex
Complete advqft2, fix some ambiguities
... about finite symmetry transformations in previous work

	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
	\begin{equation}
		S' = S
		\propto \int \dd[2]{z}
			\pd X^\mu \pdbar X_\mu
		= \int \dd[2]{z'}
			\pd' X'^\mu \pdbar' X'_\mu
%		= \int \dd[2]{z'}
%			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
	\end{equation}
	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
%	\begin{gather}
%		X'(z',\bar{z}') - \alpha'V
%		\simeq X(z,\bar{z})
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
%			},\\[1ex]
%		X\longmapsto
%		X'(z,\bar{z})
%		\simeq X\pqty\Big{
%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
%			} + \alpha'V
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
%			},
%	\end{gather}
	\begin{equation}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \order{\epsilon^3}
		}
	\end{equation}
	The above process can be done order by order, in the end we obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \frac{1}{3}\,(\pd\epsilon)^2
			- \cdots
		} + \pqty{\mrm{conjugate}} \\
		&= -\frac{\alpha' V}{2}\,
			\ln (1 + \pd\epsilon)
		+ \pqty{\mrm{conjugate}} \\[.5ex]
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}

>>>>

	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
	\begin{equation}
		S' = S
		\ \Longrightarrow\ %
		\int \dd[2]{z}
			\pd X'^\mu \pdbar X'_\mu (z,\bar{z})
		\xlongequal{(*)} \int \dd[2]{z'}
			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
		= \int \dd[2]{z}
			\pd X^\mu \pdbar X_\mu (z,\bar{z})
	\end{equation}
	Here at $(*)$ we use the diff-invariant property of the action. 
	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
%	\begin{gather}
%		X'(z',\bar{z}') - \alpha'V
%		\simeq X(z,\bar{z})
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
%			},\\[1ex]
%		X\longmapsto
%		X'(z,\bar{z})
%		\simeq X\pqty\Big{
%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
%			} + \alpha'V
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
%			},
%	\end{gather}
	\begin{equation}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \order{\epsilon^3}
		}
	\end{equation}
	The above process can be done order by order, in the end we obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \frac{1}{3}\,(\pd\epsilon)^2
			- \cdots
		} + \pqty{\mrm{conjugate}} \\
		&= -\frac{\alpha' V}{2}\,
			\ln (1 + \pd\epsilon)
		+ \pqty{\mrm{conjugate}} \\[.5ex]
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}
